Appendix 1: sdmTMB statistical model description

### 2021-12-22 doc/appendix-model.Rmd
Add code to model table

```{r symbols, results='asis'}
symbols <- tibble::tribble(
  ~Symbol, ~Description,
  "$y$", "Observed response data",
  "$\\mu$", "Mean",
  "$\\phi$", "A dispersion parameter for a distribution",
  "$f$", "Link function",
  "$f^{-1}$", "Inverse link function",
  "$\\boldsymbol{\\beta}$", "Parameter vector",
  "$\\boldsymbol{X}$", "A predictor model matrix",
  "$O_{\\s, t}$", "An offset variable at point $\\s$ and time $t$",

  "$\\omega_{\\s}$", "Spatial random field at point $\\s$ (knot)",
  "$\\omega_{\\s}^*$", "Spatial random field at point $\\s$ (interpolated)",
  "$\\zeta_{\\s, t}$", "Spatially varying coefficient random field at point $\\s$ and time $t$ (knot)",
  "$\\zeta_{\\s, t}^*$", "Spatially varying coefficient random field at point $\\s$ and time $t$ (interpolated)",
  "$\\epsilon_{\\s, t}$", "Spatiotemporal random field at point $\\s$ and time $t$ (knot)",
  "$\\epsilon_{\\s, t}^*$", "Spatiotemporal random field at point $\\s$ and time $t$ (interpolated)",
  "$\\delta_{\\s,t}$", "AR1 or random walk spatiotemporal deviations (knot)",
  "$\\alpha_g$", "IID random intercept deviation for group $g$",

  "$\\boldsymbol{\\Sigma}_\\omega$", "Spatial random field covariance matrix",
  "$\\boldsymbol{\\Sigma}_\\zeta$", "Spatially varying coefficient random field covariance matrix",
  "$\\boldsymbol{\\Sigma}_\\epsilon$", "Spatiotemporal random field covariance matrix",
  "$\\boldsymbol{Q}_\\omega$", "Spatial random field precision matrix",
  "$\\boldsymbol{Q}_\\zeta$", "Spatially varying coefficient random field precision matrix",
  "$\\boldsymbol{Q}_\\epsilon$", "Spatiotemporal random field precision matrix",

  "$\\sigma_\\alpha^2$", "IID random intercept variance",
  "$\\sigma_\\epsilon^2$", "Spatiotemporal random field marginal variance",
  "$\\sigma_\\omega^2$", "Spatial random field marginal variance",
  "$\\sigma_\\zeta^2$", "Spatially varying coefficient random field marginal variance",
  "$\\kappa_\\omega$", "Spatial decorrelation rate",
  "$\\kappa_\\epsilon$", "Spatiotemporal decorrelation rate",

  "$\\rho$", "Correlation between random fields in subsequent time steps",
  "$\\boldsymbol{A}$", "A sparse projection matrix to bilinearly interpolate between knot and data locations",
  "$\\boldsymbol{H}$", "A 2-parameter rotation matrix used to define anisotropy"
)
knitr::kable(symbols, caption = "Symbol notation and descriptions.", escape = FALSE, format = "latex", booktabs = TRUE,
   linesep = c(
    rep('', 7), # y, mean etc.
    '\\addlinespace',
    rep('', 7), # fields
    '\\addlinespace',
    rep('', 5), # covariance stuff
    '\\addlinespace',
    rep('', 5), # more covariance stuff
    '\\addlinespace',
    rep('', 99) # end
  ))
```

>>>>

```{r symbols, results='asis'}
symbols <- tibble::tribble(
  ~Symbol, ~Code, ~Description,
  "$y$", "\\texttt{y\\_i}", "Observed response data",
  "$\\mu$", "\\texttt{mu\\_i}", "Mean",
  "$\\phi$", "\\texttt{phi}", "A dispersion parameter for a distribution",
  "$f$", "\\texttt{fit\\$family\\$link}", "Link function",
  "$f^{-1}$", "\\texttt{fit\\$family\\$linkinv}", "Inverse link function",
  "$\\boldsymbol{\\beta}$", "\\texttt{b\\_j}", "Parameter vector",
  "$\\boldsymbol{X}$", "\\texttt{X\\_ij}", "A predictor model matrix",
  "$O_{\\s, t}$", "\\texttt{offset}", "An offset variable at point $\\s$ and time $t$",

  "$\\omega_{\\s}$", "\\texttt{omega\\_s}", "Spatial random field at point $\\s$ (knot)",
  "$\\omega_{\\s}^*$", "\\texttt{omega\\_s\\_A}", "Spatial random field at point $\\s$ (interpolated)",
  "$\\zeta_{\\s, t}$", "\\texttt{zeta\\_t}", "Spatially varying coefficient random field at point $\\s$ and time $t$ (knot)",
  "$\\zeta_{\\s, t}^*$", "\\texttt{zeta\\_t\\_A}", "Spatially varying coefficient random field at point $\\s$ and time $t$ (interpolated)",
  "$\\epsilon_{\\s, t}$", "\\texttt{epsilon\\_st}", "Spatiotemporal random field at point $\\s$ and time $t$ (knot)",
  "$\\epsilon_{\\s, t}^*$", "\\texttt{epsilon\\_st\\_A}", "Spatiotemporal random field at point $\\s$ and time $t$ (interpolated)",
  "$\\delta_{\\s,t}$", "\\texttt{b\\_t}", "AR1 or random walk spatiotemporal deviations (knot)",
  "$\\alpha_g$", "\\texttt{RE}", "IID random intercept deviation for group $g$",

  "$\\boldsymbol{\\Sigma}_\\omega$", "\\texttt{-}", "Spatial random field covariance matrix",
  "$\\boldsymbol{\\Sigma}_\\zeta$", "\\texttt{-}", "Spatially varying coefficient random field covariance matrix",
  "$\\boldsymbol{\\Sigma}_\\epsilon$", "\\texttt{-}", "Spatiotemporal random field covariance matrix",
  "$\\boldsymbol{Q}_\\omega$", "\\texttt{Q\\_s}", "Spatial random field precision matrix",
  "$\\boldsymbol{Q}_\\zeta$", "\\texttt{Q\\_s}", "Spatially varying coefficient random field precision matrix",
  "$\\boldsymbol{Q}_\\epsilon$", "\\texttt{Q\\_st}", "Spatiotemporal random field precision matrix",

  "$\\sigma_\\alpha^2$", "\\texttt{sigma\\_G}", "IID random intercept variance",
  "$\\sigma_\\epsilon^2$", "\\texttt{sigma\\_E}", "Spatiotemporal random field marginal variance",
  "$\\sigma_\\omega^2$", "\\texttt{sigma\\_O}", "Spatial random field marginal variance",
  "$\\sigma_\\zeta^2$", "\\texttt{sigma\\_Z}", "Spatially varying coefficient random field marginal variance",
  "$\\kappa_\\omega$", "\\texttt{kappa(0)}", "Spatial decorrelation rate",
  "$\\kappa_\\epsilon$", "\\texttt{kappa(1)}", "Spatiotemporal decorrelation rate",

  "$\\rho$", "\\texttt{ar1\\_rho}", "Correlation between random fields in subsequent time steps",
  "$\\boldsymbol{A}$", "\\texttt{A}", "Sparse projection matrix to interpolate between knot and data locations",
  "$\\boldsymbol{H}$", "\\texttt{H}", "2-parameter rotation matrix used to define anisotropy"
)
knitr::kable(symbols, caption = "Symbol notation, code representation (in model output or in model template code), and descriptions.", escape = FALSE, format = "latex", booktabs = TRUE,
   linesep = c(
    rep('', 7), # y, mean etc.
    '\\addlinespace',
    rep('', 7), # fields
    '\\addlinespace',
    rep('', 5), # covariance stuff
    '\\addlinespace',
    rep('', 5), # more covariance stuff
    '\\addlinespace',
    rep('', 99) # end
  ))
```
